Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-08-24 Paper/gammaRays.tex
Added Intro to Cosmology appendix

\section{Cosmology}
Before calculating light curves and stretching factors, we will need some equations from cosmology.

>>>>

\section{Cosmology}
This appendix contains a few formulas we need from cosmology, in particular the area of a photon sphere $A_{ph}\left(z\right)$, a sphere over which photons emitted in a particular burst at redshift $z$ are spread; and the volume of the infinitesimal shell surrounding a burst sphere $\dif V\left(z\right)$, a sphere over which bursts at redshift $z$ are distributed.
